X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2013-10-31 hedpc_natphys.tex
abstract typos

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match beam
    divergence and allow large field of views on a short and efficient
    setup.
\end{abstract}
\maketitle

>>>>

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}
\maketitle
